---
title: "linear model from Web"
author: "Alondra"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction
We predict a simulated strength score base on arm and grip strength. We will fine 3 models and compare them. The response variable is numerical, and the explanatory variable is numerical, so we use the num~num helper file.

## Model 1 SIM~ARMS

## Results
### Graphical Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```
This graph shows that as arm strength goes up, the simulation score goes up as well. 

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation is 0.69 which shows that arm strength is related to sim score. 

### Infrential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
Both the intercept and the coefficent of arm strength are significantly different from zero.


### Prediction Interval
```{r}
newdata= data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```
The prediction interval is from -1.7 to 3.1 for SIM score. 


## Model 2 SIM~GRIP

## Results
### Graphical Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='red')
```
This graph shows that as grip strength goes up, the simulation score goes up as well. The points along the regression line in the grip plot is more spread out than the arm strength plot. 

### Numerical results 
 
```{r}
cor(SIMS~GRIP,data=data)
```
The correlation is 0.63 which shows that girp strength is related to sim score.

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
Both the intercept and the coefficent of grip strength are significantly different from zero.

## Prediction Interval

```{r}
newdata= data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```
The prediction interval is from -3.1 to 2.0 for the sim score. 

## Model 3 SIM~ARM+GRIP

### Numerical Results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation is 0.73 which shows that arm and grip strength is related to sim score. 

### Infrential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```
Both the intercept and the coefficent of grip and arm strength are significantly different from zero.


### Prediction Interval
```{r}
newdata= data.frame(ARM=88, GRIP=94)
predict(model.3, newdata, interval="predict")
```
The prediction interval is from -2.1 to 2.4 for SIM score. 


## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
anova(model.3,model.1)
```
The p-value is .00000499 so I reject the null hypothesis. Model 1 is better than model 2 because the rss for model 1 is smaller.

```{r}
anova(model.3,model.2)
```
Model 3 is smaller than model 2 because the rss for model 3 is smaller


# Discussion and Conclusion

Out of the three models, model 3 is the best because it has a smaller rss. 




